Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/Supplementary.tex
wworking on supp

\section{Movie Descriptions}
We consider suspensions of JPs of radius 1.25~nm. The time step size for
all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
%\mbox{} \\

@@

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
%\newpage

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{Shear Flow cases}}\par\medskip
\textbf{Type I, bilayer phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
%The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ulshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ulshraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type II, multilamellar phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under shear flow with choices of shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type III, striated phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{TG Flow Cases}}\par\medskip
\textbf{Type I, bilayer  phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, vesicle bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type II, multilamellar phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under TG flow with choices of shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type III, striated phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under TG flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:sttgraw}
\end{figure}

>>>>

\section{Movie Descriptions}
\label{sec:movie_description}
We consider suspensions of JPs of radius 1.25~nm. The time step size for
all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
%\mbox{} \\

@@

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and
striated JP configurations under shear flow (Supplementary
Figures~\ref{fig:ulshraw}--\ref{fig:stshraw}) and under TG flow
(Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$, panels
(b) for alignment $S_2$, and panels (c) are for strain $E$ (as a
percentage).  A common ordinate is used for each of the respective
panels to facilitate comparison between data sets. 
%\newpage

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{Shear Flow cases}}\par\medskip
\textbf{Type I, bilayer phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
  rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
%The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ulshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
  rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.  The JP type is the same
  as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
  configuration rather than a
  disordered bilayer.  
%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type II, multilamellar phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type II, multilamellar phase under shear flow with
  shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type III, striated phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
  (c) strain $E$ for Type III, striated phase under shear flow with
  shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{TG Flow Cases}}\par\medskip
\textbf{Type I, bilayer  phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under TG flow with shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, vesicle bilayer phase under TG flow with shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type II, multilamellar phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under TG flow with shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type III, striated phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under TG flow with shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:sttgraw}
\end{figure}
